COG-ED Manuscript

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
corrected double brackets

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI [`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`]

>>>>

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`
